---
title: "Final Project"
author: "Charles Onesti, Thuan Tran, Cole Raines"
date: "Date"
output: pdf_document
---
  
  
```{r, echo=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

# Introduction

Intro paragraph(s) here:

- What is your research question? 
- Why do we care/why is it interesting? 
- What are your hypotheses? 
- What method will you use to test these hypotheses?


# Data Section

```{r, echo = FALSE}
# Read in your dataset here
hpop <- read.csv("Spring 19 data.csv")

# If you are cleaning any data, clean it here

names(hpop)[names(hpop) == "Which.of.the.following.best.describes.the.area.in.which.you.live..if.in.college..when.not.in.school.."] <- "urbanization"
names(hpop)[names(hpop) == "Education..Categorical."] <- "education"
names(hpop)[names(hpop) == "Which.of.the.following.statements.comes.closest.to.your.view.regarding.climate.change."] <- "climate_opinion"
names(hpop)[names(hpop) == "Household.Income"] <- "income"
names(hpop)[names(hpop) == "X.Most.important..Which.of.the.following.do.you.consider.to.be.the.most.and.second.most.important.goals.of.U.S..foreign.policy."] <- "first"
names(hpop)[names(hpop) == "X.Second.most.important..Which.of.the.following.do.you.consider.to.be.the.most.and.second.most.important.goals.of.U.S..foreign.policy."] <- "second"


hpop_clean = subset(hpop, select = c(education, income, urbanization, climate_opinion, first, second))

hpop_clean$climate <- ifelse(hpop_clean['climate_opinion'] == "It's a crisis and demands urgent action", 3, ifelse(hpop_clean['climate_opinion'] == "It's a problem, but we don't need urgent action now; other issues are more important", 2, ifelse(hpop_clean['climate_opinion'] == "It's not a problem; attempting to address is will be harmful to the economy", 1, NA)))

hs <- subset(hpop_clean, hpop_clean$education == "High school")
lesshs <- subset(hpop_clean, hpop_clean$education == "Less than high school")
someColl <-subset(hpop_clean, hpop_clean$education == "Some college")
bacc <- subset(hpop_clean, hpop_clean$education == "Bachelor's degree or higher")


```

Data explanation here:

We are using the Harvard Public Opinions Poll dataset.  Our sample has 3022 units and 196 variables.  In our study, we only look at information from 6 of these variables. 


- What dataset(s) are you using? 
    + What is the size of your sample?
    + What is the unit of analysis?
    + What is your research design (cross sectional, randomized experiment, etc)
- What is your dependent variable and how is it coded? If you cleaned your data in some way, how did you do it? (i.e. recoded data from percent to decimal, dropped some irrelevant responses, etc.)

```{r, echo = FALSE}
# Dependent variable summary statistics here

```


```{r, echo = FALSE}
# Dependent variable plot here

```

- What is your independent variable and how is it coded? If you cleaned your data in some way, how did you do it? (i.e.. recoded data from percent to decimal, dropped some irrelevant responses, etc.)

```{r, echo = FALSE}
# Independent variable summary statistics here

```


```{r, echo = FALSE}
# Independent variable plot here

```

- Are you considering any confounders? How are they coded?


# Results

Your results paragraphs should answer the following questions:

- What is the observed relationship when you plot it?

```{r, echo = FALSE}
# Scatter plot here


averages_education <- c('Less than HS diploma' = mean(lesshs$climate), 'HS Diploma' = mean(hs$climate), 'Some College' = mean(someColl$climate), 'Bachelors or Higher' = mean(bacc$climate))

barplot(xlab = 'Education Level', ylab = 'Climate Attitude', ylim = c(0,3), averages_education)
```

- If using linear model: what are your bivariate regression results? Interpret your coefficient of interest, and comment on the statistical significance. Do you think your result represents a causal effect?

```{r, echo = FALSE}
# Bivariate regression results here

```

- Do your results change when you add confounders? Interpret your coefficient of interest, and comment on the statistical significance. Do you think your result represents a causal effect?

```{r, echo = FALSE}
# Multivariate regression results here

```


# Conclusion

- Summarize your findings. Is your hypothesis supported by your results?
- What are some limitations to your analysis? Do you think you have identified a causal effect? Why or why not?
- How can your analysis be improved if you had access to unlimited data?


# Individual contributions

- Please note each team member's contribution to the final product here.
